Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
paper beautification

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$ seconds, and most controllers can be synthesized in less
than $17.2$ seconds. We further show that, in a direct comparison, the abstraction-based
approach lowers the median runtime of our benchmarks by a factor of seven over the
multi-staged approach.

@@

%\todo{Have we covered all the literature by Feron et al?}

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses bounded-input and bounded-output (BIBO) properties to determine stability, 
the latter uses Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}.
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

@@

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.  
There are several cases for which the system may fail to find a controller. In the naive approach,
there is the risk of the completeness threshold being too large, thus causing a timeout.
In the abstraction case, there is the risk of requiring a very precise abstraction, resulting in too many refinements which may timeout.
Other sources for incompleness are the inability of the {\sc synthesize} phase to use a large enough precision for the plant model in a given problem.

@@

We have presented two approaches to synthesize state feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the system's dynamics 
up to the completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
Both approaches are novel in the control system literature in that it puts
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering the various error sources in the implementation 
of the control algorithm and in the computational modeling of plant dynamics.
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a reasonable
amount of time fully automatically.  In particular, both approaches
complement each other and together solve all benchmarks provided in the set.
Future work will be the extension of these approaches to consider performance 
requirements while synthesizing digital controllers and the application of them
for synthesizing state observers that generally appears in state feedback 
architecture.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Discretizing continuous space dynamics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is $7.9$ seconds, and most controllers can be synthesized in less
than $17.2$ seconds.

@@

\todo{Have we covered all the literature by Feron et al?}

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A~more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilization as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.

@@

\item Calculate the noise set $N$ from the quantizer resolutions and estimated round-off errors: %($\frac{q_1}{2},\frac{q_2}{2},q_3$)
$$N=\left \{ \nu_1+\nu_2+ \nu_3 : \nu_1 \in \left[-\frac{q1}{2}\ \ \frac{q1}{2}\right] 
\wedge \nu_2 \in \left[-\frac{q2}{2}\ \ \frac{q2}{2}\right]  \wedge \nu_3 \in \left[-q3\ \ q3\right]  \right \}\nonumber$$
where $q3$ is the maximum truncation and rounding error of $u_k=-K\hat{x}_k$ as discussed in section \ref{sec:numeric_rep}
More details on how to model quantization as noise are given in the 
Appendix~\ref{appendix:quantization-noise}.
\item Calculate a set of initial bounds on $K$, $\phi_{init}^{K}$, based on the input constraints. Note that these bounds will be used by the {\sc synthesize} phase to reduce the size of the solution space.
$$(\phi_{init} \wedge u_k=-K x_k) \Rightarrow \phi_{init}^{K}$$

@@

The median runtime for our benchmark set is 7.9\,s.  Overall,
the average synthesis time amounts to approximately 17.2\,s.  We
consider these times short enough to be of practical use to control
engineers, and thus affirm RQ1.

@@

We have presented two automated approaches to synthesize digital state-feedback controllers 
that ensure both stability and safety over the state-space representation.
The first approach relies on explicit unfolding of the closed-loop model dynamics 
up to a completeness threshold, whilst the second one applies abstraction 
refinement and acceleration to increase speed whilst retaining soundness.
%
Both approaches are novel within the control literature: they put 
forward a fully automated synthesis approach that is algorithmically and
numerically sound, considering various error sources in the implementation 
of the digital control algorithm and in the computational modeling of plant dynamics. 
%
Our experimental results show that both approaches are able
to synthesize stable controllers in most benchmarks within a small 
amount of time automatically.  In particular, both approaches 
complement each other and together solve all benchmarks, which have been derived from the control literature.

Future work will focus the extension of these approaches to output-based control architectures (hinging on the use of observers), 
and to considering performance requirements (alongside safety) in the synthesis of digital controllers.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Time discretization of continuous-space dynamics}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
